---
title: "CARPS_EXT_24-4-2015 CLASSS"
author: "Kengthsagn Louis"
date: "11/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("devtools") 
devtools::install_github("METRICS-CARPS/CARPSreports")
library(CARPSreports)

#Methods
#Participants read a description of an angular momentim and then completed a pretest of 52 trials (and 6 practice trials) with the following two-forced questions: 
#1. “Did Woody experience more or less force than the Template?”
#2. “Are the forces in the same or in different directions?”

#They were then assigned to either an action group or an observation group to receive ten minutes training. They then answered the same two forced questions as a posttest. 

##Target Outcomes
#As copied directly from the article: Pretest performance did not differ as a function of group, as revealed by a one-way analysis of variance (ANOVA), F(1, 42) = 0.01, p > .250 (see Fig. 2, left panel). However, an ANOVA controlling for pretest accuracy revealed that group did have a significant effect on posttest performance, F(1, 41) = 5.21, p = .028, ηp 2 = .113. Students in the action group showed a significantly nonzero (~10%) gain in accuracy from pretest to posttest, t(21) = 3.07, p = .006. Those in the observation group did not, t(21) = –0.01, p > .250 (see Fig. 2, left panel).

library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(devtools)
install.packages("CARPSreports") #Says Warning in install.packages :Package ‘CARPSreports’ is not available (for R version 3.5.1)

```{r echo=TRUE}
load("~/Desktop/Stanford Year 1/Fall 2018/Methods 251/Reproducibility HW/CARPS_EXT_24-4-2015_CLASS/data/study 1 physics_dataverse.RData")
View (x)
structure(x)
head(x)
colnames(x)
table(x$group)
```

#Calculate ANOVA as a function of group (action or obervation)

To see if pretest varies as a function of group.

```{r echo=True}
#Caculate means
##1)Create a new column to transform group into a numeric value such that action = 1, and observation =2
x = x %>%
  mutate(numeric_group=as.numeric(group))
View(x)
##Still need to calculate the mean

##2)Visualize the data
ggplot(x, aes(x=group, y=mag1, fill=group)) +
geom_bar(position="dodge", stat="identity") + 
labs(title = "Pretest differences in perfomance as a function of group", y = "Performance means", x= "Group")+
scale_fill_brewer(palette="Set1")

##4)Now the on-way ANOVA to see if to see if pretest performance varies as a function of group
summary(aov(mag1~numeric_group,data=x))

#The result for this is non-sginificant, but I am getting slightly different numbers. I probbaly made a mistake in somehwehere. 
#My results: F(1,42)=.015, p=.903
#The reported results in the article: F(1, 42) = 0.01, p > .250

#Let's see what the F statistic is if I used lm instead of aov
summary(lm(mag1~numeric_group,data=x))

#My results are still the same: F(1,42)=.01491  p=.903 is consistent with what I found when I ran the one way anova using the aov function. 
```


##Control for pretest accuracy and calculate postest performance using ANCOVA
```{r echo=True}
perf1 <- aov (mag1~ mag2*numeric_group, data=x)#the covariate here is mag1 
summary(perf1)

#Had to install the broom package to run the TukeyHSD test
thsd <-TurkeyHSD(perf1,"numeric_group", ordered=TRUE)
```
#T-test for pretest to postest performance for action group 
```{r echo=True}
t-test <-
mutate(group_by(numeric_group)) %>%
t.test(mag_improvement~numeric_group, data = x, paired = TRUE)
```
#T-test for pretest to postest performance for observation group
```{r echo=True}

```